Detection and replication of epistasis influencing transcription in humans

### 2013-09-23 docs/manuscript/manuscript.tex
manuscript is sent for appeal but now making changes in the meantime

\begin{figure}[H]
	\centering
	\includegraphics[width=5in]{pale_gray_graph_of_interactions_2_lists_GrayEdges}
	\caption{\textbf{Discovery and replication of epistatic networks} All 434 putative genetic interactions (edges) with data common to discovery and replication sets is shown, where black nodes represent SNPs and red nodes represent traits (gene expression probes). Three hundred and forty-five interactions had $p$-values exceeding the 2.5\% confidence interval following meta analysis of the replication data The remaining 89 interactions that did not replicate are depicted in grey. It is evident that a large proportion of the complex networks identified in the discovery set also exist in independent populations.}
	\label{fig:fireworks}
\end{figure}

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=5in]{pale_gray_graph_of_interactions_2_lists_GrayEdges}
	\caption{\textbf{Discovery and replication of epistatic networks} All 434 putative genetic interactions (edges) with data common to discovery and replication sets is shown, where black nodes represent SNPs and red nodes represent traits (gene expression probes). Three hundred and forty-five interactions had $p$-values exceeding the 2.5\% confidence interval following meta analysis of the replication data The remaining 89 interactions that did not replicate are depicted in grey. It is evident that a large proportion of the complex networks identified in the discovery set also exist in independent populations. An interactive version of this graph can be found here: }
	\label{fig:fireworks}
\end{figure}
